---
title: "Homework 6"
format: 
  pdf:
    document: default
    keep-tex: false
    fig-width: 6.5      
    fig-height: 8        
    code-fold: false    
execute:
  echo: false  
bibliography: hw6.bib
---


## Load the data


```{r}
library(here)
data <- read.csv(here("data", "star.csv"))

```

Here is an in-text citation: @tanner2015. Here is our second citation [@Here].

\newpage

## Commit 3
#### Write the code to create the summary statistics shown in the table below. Output the table below and briefly describe it in text.

```{r}
library(tidyverse)
library(rio)
library(knitr)
library(kableExtra)

data_table <- data %>%
  group_by(sex, frl) %>% 
  summarize(
    math_mean = round(mean(tmathss, na.rm = TRUE), 2),
    math_sd = round(sd(tmathss, na.rm = TRUE), 2),
    rdg_mean = round(mean(treadss, na.rm = TRUE), 2),
    rdg_sd = round(sd(treadss, na.rm = TRUE),2)) %>% 
   kable() %>% 
   kableExtra::row_spec(0, background = "white", bold = TRUE) %>% 
   kableExtra::row_spec(1:4, background = "white")


data_table

```

I created a simple table with white background and bolded headers. The table has 4 rows and 6 columns. I also rounded all of the means and standard deviations to two decimal places, to match the table provided as a guide. By looking at this table we can see that the highest mean reading score is girls without free/reduced lunch, and the highest mean math score is also girls without free/reduced lunch. 

\newpage

# References